\Title

### 2021-05-28 manuscript/content.tex
Add more content to Australia section in manuscript

We start the interpolation process by defining a set of block-averaged sources
at a relative depth of \AustraliaEqlDepth{} and a block size of
1.8\km{}, resulting in a total of \AustraliaEqlNSources{}~point
sources.
The block size was chosen to match the desired resolution of the final grid
 (1~arc-minute is approximately 1.8\km{} at the equator).
The coefficients of the gradient-boosted equivalent sources are estimated using
a damping equal to \AustraliaEqlDamping{} and a window size of
\AustraliaEqlWindowSize{}, which was chosen in order to limit the amount of
computer memory needed to store the Jacobian matrix to under 10~Gigabytes.
Finally, we used the estimated source coefficients to predict the values of the
gravity disturbance on a regular grid of
\AustraliaEqlGridNLongitude{}$\times$\AustraliaEqlGridNLatitude{} points at
\AustraliaEqlGridHeight{} above the ellipsoid.
Fig.~\ref{fig:australia} shows the original data distribution and the
interpolated regular grid.
Grid points that are further than 50\km{} from the nearest data
point are masked to avoid unrealistic extrapolations.

@@

@@

The gradient-boosted equivalent sources implementation is based on the
equivalent source code in the Harmonica library \citep{harmonica2020}.
Other software used in this study includes:
Pooch \citep{pooch2020} for downloading and caching datasets,
Verde \citep{verde2018} for block reductions and coordinate manipulations,
Boule \citep{boule2020} for normal gravity calculations,
xarray \citep{xarray2017} and Numpy \citep{numpy2020} for handling
multidimensional arrays and numerical computations,
Numba \citep{numba2015} for just-in-time compilation and parallelization,
Matplotlib \citep{matplotlib2007} and PyGMT \citep{pygmt2020} for generating
the figures and maps,
and the Jupyter notebook programming environment \citep{jupyter2016}.
Harmonica, Boule, Pooch, and Verde are part of the Fatiando a Terra project
\citep{fatiando2013}.

>>>>

We start the interpolation process by defining a set of block-averaged sources
using a block size of 1.8\km{}, resulting in a total of
\AustraliaEqlNSources{}~point sources which depths remain unknown for now.
The block size was chosen to match the desired resolution of the final grid
 (1~arc-minute is approximately 1.8\km{} at the equator).
Then we need to determine the size of the windows that will be used for
estimating the coefficients of the gradient-boosted equivalent sources.
We computed the amount of computer memory needed in order to store the largest
Jacobian matrix for different values of window size
(Fig.~\ref{fig:australia-memory-cv-error}a).
We have chosen a window size of \AustraliaEqlWindowSize{} in order to limit the
amount of memory needed to under 16~Gigabytes.

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/australia-memory-cv-error.pdf}
    \caption{
        (a) Amount of computer memory needed to store the largest Jacobian
        matrix vs different window sizes. Each memory requirement corresponds
        to the ammount of memory needed to store the elements of the largest
        Jacobian matrix during the process of estimating the gradient-boosted
        equivalent sources coefficients, using a double precision floating
        point for each (64 bits).
        (b) Root-mean square errors obtained after the K-Fold cross-validation
        for each pair of damping and depth parameters. The orange
        square highlights the minimum RMS value.
        (c) Root-mean square error of the residue after each iteration of the
        coefficients estimation process.
    }
    \label{fig:australia-memory-cv-error}
\end{figure*}

Secondly, we need to determine the depth of the sources and the value for the
damping parameter. Based on the results obtained in
Section~\ref{sec:synthetic_distributions}, we have chosen to locate them using
the \emph{relative depth} strategy.
In order to determine the values for the \emph{depth} and \emph{damping}
parameters, we have applied a K-Fold cross-validation method through the
scikit-learn implementation \citep{sklearn2011}.
It consists in randomly dividing the original data into $k$ small sets (or
folds), estimate the source coefficients using only $k - 1$ of the folds
(training data) and validate the model by comparing its predictions with the
remaining fold (testing data). This process is carried out once for each one of
the $k$ folds.
With the goal of speeding up the computations, we selected a portion of the
Australia gravity disturbances to run the cross-validation: an area of
\AustraliaSmallAreaEastingSize{}$\times$\AustraliaSmallAreaNorthingSize{}
containing \AustraliaSmallAreaNPoints points.
We run the cross-validation with a combination of \emph{depth} ranging from
\AustraliaDepthMin{} to \AustraliaDepthMax{},
and \emph{damping} from
\AustraliaDampingMin{} to \AustraliaDampingMax{} in steps of one order of
magnitude.
We have used the root-mean square error as the validation function between the
testing data and the predictions on each k-fold and computed the mean of all
the RMS for each combination of the \emph{depth} and \emph{damping} parameters.
Figure \ref{fig:australia-memory-cv-error}b shows the resulting scores of the
cross-validation and highlights the minimum value achieved:
\AustraliaEqlRmsScore{} corresponding to a relative depth of \AustraliaEqlDepth{} and
a damping equal to \AustraliaEqlDamping{}.

Finally, we proceed to estimate the coefficients of the whole set of
gradient-boosted equivalent sources using the parameters previously determined.
Fig.~\ref{fig:australia-memory-cv-error}c shows the root-mean square of the
residue after each iteration of the gradient-boosting algorithm, exposing how
to algorithm converges at a minimum difference between the gravity disturbance
data and the predicted values by the equivalent sources.
We then used the estimated source coefficients to predict the values of the
gravity disturbance on a regular grid of
\AustraliaEqlGridNLongitude{}$\times$\AustraliaEqlGridNLatitude{} points at
\AustraliaEqlGridHeight{} above the ellipsoid.
Fig.~\ref{fig:australia} shows the original data distribution and the
interpolated regular grid.
Grid points that are further than 50\km{} from the nearest data
point are masked to avoid unrealistic extrapolations.

Fig.~\ref{fig:australia-residuals} shows the residuals on each observation
point: the difference between the gravity disturbance data and the predicted
values by the equivalent sources on the same points.
The inset figure shows a histogram of the residual values, depicting that the
residuals are normally distributed around zero.

@@

\begin{figure}
    \includegraphics[width=\linewidth]{figs/australia-residuals.png}
    \caption{
        Residuals. Differences between the gravity disturbance data from
        Australia and the predicted values by the estimated equivalent sources
        on the same observation points. The color map has been truncated to
        improve the visualization around the largest portion of residual
        values. The inset plot shows a histogram of the residuals.
    }
    \label{fig:australia-residuals}
\end{figure}

@@

The gradient-boosted equivalent sources implementation is based on the
equivalent source code in the Harmonica library \citep{harmonica2020}.
Other software used in this study includes:
Pooch \citep{pooch2020} for downloading and caching datasets,
Verde \citep{verde2018} for block reductions and coordinate manipulations,
Boule \citep{boule2020} for normal gravity calculations,
xarray \citep{xarray2017} and Numpy \citep{numpy2020} for handling
multidimensional arrays and numerical computations,
Numba \citep{numba2015} for just-in-time compilation and parallelization,
scikit-learn \citep{sklearn2011} for cross-validation,
Matplotlib \citep{matplotlib2007} and PyGMT \citep{pygmt2020} for generating
the figures and maps,
and the Jupyter notebook programming environment \citep{jupyter2016}.
Harmonica, Boule, Pooch, and Verde are part of the Fatiando a Terra project
\citep{fatiando2013}.
